Benchmarking KiCS2

### 2014-11-14 benchmarks/benchmark_papers/kics2/bench_kics2.tex
Comments updated
Benchmarks expanded with dist infos
Benchmarks extended with section on constraint store usage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a paper to benchmark various versions of the KiCS2 system.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a paper to benchmark various versions of the KiCS2 system
% and compare its efficiency with other Curry systems (PAKCS, MCC).
%
% This can be executed and formatted by the command
% > ../execpaper -f bench_kics2.tex
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The benchmarks are executed with various Curry systems.
The following table summarizes some information about the
actual back ends of these systems.

\begin{center}
\runcurry{distInfosAsTable (PAKCS:kics2Systems++[KiCS2Local []])}
\end{center}

@@

\subsection{Binding Benchmarks for KiCS2}

The following benchmarks demonstrate the relevance of the
constraint store of KiCS2. They compare PAKCS with a local installation
of KiCS2 where KiCS2 runs either in standard mode and
in a mode where the constraint store is disabled by the option
\begin{quote}
\texttt{:set ghc -DDISABLE\_CS -fforce-recomp}
\end{quote}

\begin{center}
\runcurry{mainBench [PAKCS, KiCS2Local [], KiCS2Local [WithoutCS]] bindingBench}
\end{center}
